Data Preparation

### 2019-01-09 Data Preparation.Rmd
Adding additional variables at the course level

>>>>

Finally, we add a series of informative variable at the course level.
```{r}
d_course <- d_course %>%
  mutate(
    `Missing from ILO File` = as.logical(`Missing from ILO File`),
    Letters = substring(Code, 1, 3),
    Number  = as.numeric(substring(Code, 4, 7)),
    Level   = case_when(between(Number, 1000, 1999) ~ "Introductory",
                        between(Number, 2000, 2999) ~ "Intermediate",
                        between(Number, 3000, 3999) ~ "Advanced"    ))
print(select(d_course, Code, Letters, Number, Level))
```
